Hydra Battles in Coq

### 2020-11-08 doc/hydras.tex
minor corrections

In some cases we want to show that two notation systems describe the same segment (for instance $[0,3+\omega)$ and $[0,\omega($\;). For this purpose, one may prove that the two notation systems are order-isomorphic.

@@

\begin{exercise}
Let $i$ be some natural number. Prove that the notation systems 
\texttt{Omega} and \texttt{ON\_plus (OrdFin $i$) Omega} are isomorphic.

{\it \textbf{Note:} This property reflects the equality $i+\omega=\omega$, that we will prove in larger notation systems, as well as in Schütte's model.}

@@

For instance, the
elements of the product \texttt{ON\_mult Omega (FinOrd 3)} are ordered as follows.
\[(0,0),(0,1),(0,2),(0,3),(0,4),\dots,{\color{red}(1,0),} (1,1),(1,2),\dots, {\color{red}(2,0)},(2,1),(2,2),\dots\]

>>>>

In some cases we want to show that two notation systems describe the same segment (for instance $[0,3+\omega)$ and $[0,\omega)$\;). For this purpose, one may prove that the two notation systems are order-isomorphic.

@@

\begin{exercise}
Let $i$ be some natural number. Prove that the notation systems 
\texttt{Omega} and (\texttt{ON\_plus (OrdFin $i$) Omega}) are isomorphic.

{\it \textbf{Note:} This property reflects the equality $i+\omega=\omega$, that we prove amso in larger notation systems, as well as in Schütte's model.}

@@

For instance, the
elements of the product (\texttt{ON\_mult Omega (FinOrd 3)}) are ordered as follows.
\[(0,0),(0,1),(0,2),(0,3),(0,4),\dots,{\color{red}(1,0),} (1,1),(1,2),\dots, {\color{red}(2,0)},(2,1),(2,2),\dots\]
